A higher dimensional Segal--Sugawara construction

### 2025-05-20 segalsugawara.tex
major push

\usepackage{macros-master,amsaddr,physics}
\usepackage{mathbbol}

\addbibresource{refs}

\renewcommand{\div}{\del_{\Omega}}
\renewcommand{\PV}{\mathrm{PV}}
\renewcommand{\op}{\operatorname}

\newcommand{\sfa}{\mathsf{a}}
\newcommand{\sfb}{\mathsf{b}}
\newcommand{\sfc}{\mathsf{c}}
\newcommand{\bfa}{\mathbf{a}}
\newcommand{\bfc}{\mathbf{c}}
\newcommand{\bfk}{\mathbf{k}}

\newcommand{\fields}{\cC}
\newcommand{\Vir}{\sV\op{ir}}
\newcommand{\vir}{\lie{vir}}
\setcounter{tocdepth}{1}

@@

Let $X$ be a complex manifold of dimension $n$.
The sheaf of holomorphic vector fields has the natural structure of a sheaf of Lie algebras with bracket the Lie bracket of vector fields.
Since this bracket involves only holomorphic differential operators, it extends to a bracket on the Dolbeault complex $\Omega^{0,\bu}(X,\T_X)$ of the holomorphic tangent bundle.
This bracket endows the Dolbeault complex $\Omega^{0,\bu}(X, \T_X)$ with coefficients in the holomorphic tangent bundle with the structure of a dg Lie algebra where the differential is $\dbar$.

As defined in \cite{CG2}, a local dg Lie algebra is a $\Z$-graded complex of vector bundles whose sheaf of sections is equipped with the structure of a dg Lie algebra.
Let $\cT_X$ be the local dg Lie algebra whose underlying complex of vector bundles is
\beqn
\Omega^{0,\bu}(X, \T_X) .
\eeqn
The differential is the $\dbar$-operator associated to the holomorphic bundle $\T_X$.
The bracket is the Lie bracket of holomorphic vector fields extended to the Dolbeault complex as described above.
By Dolbeault's theorem, for $U \subset X$ a Stein open set there is a quasi-isomorphism $\cT_X(U) \simeq \op{Vect}^{hol}(U)$, the Lie algebra of holomorphic vector fields on~$U$.
When $X = \C^n$ we denote $\cT_X = \cT$ for simplicity.

@@

In particular, the dg Lie algebra $\cT(\C - \{0\})$ is quasi-isomorphic to holomorphic vector fields on $\C^\times$.
Replacing $\C^\times$ by the formal punctured disk gives the Witt algebra $\Vect(D^\times) = \C((z)) \del_z$ whose unique nontrivial central extension is the Virasoro Lie algebra.

For an example of a complex manifold which is not Stein consider $X = \C^n - \{0\}$.
There is an embedding of dg Lie algebras
\beqn
\Vect^{hol}(\C^n - \{0\}) \hookrightarrow \cT(\C^n - \{0\})
\eeqn
which is no longer a quasi-isomorphism.
This map does define an isomorphism in $H^0$ cohomology, but $\cT(\C^n-\{0\})$ also has cohomology in degree $(n-1)$. 
In standard coordinates, cochain representatives for this cohomology are given by expressions of the form
\beqn
\sum_j \left(\sum_{k_1 \cdots k_n} a^j_{k_1\cdots k_n} L_{\del_{z_1}^{k_1}} \cdots L_{\del_{z_n}^{k_n}} \omega_{BM}\right) \frac{\del}{\del z_j} 
\eeqn
Here $a^j_{k_1\cdots k_n}$ are constants and $\omega_{BM} \in \Omega^{0,n-1}(\C^n-\{0\})$ is the Bochner--Martinelli form which is characterized by the formula $\oint_{S^{2n-1}} \omega_{BM} \wedge \d^n z= 1$ with $S^{2n-1}$ the sphere of radius one centered at $0 \in \C^n$.

Here we make the distinction between $\C^n$ and affine space $\A^n$; the latter is the algebraic variety with functions $\C[z_1,\ldots,z_n]$.
There is an algebraic version of $\cT(\C^n - \{0\})$ with $\C^n - \{0\}$ replaced by punctured $n$-dimensional algebraic affine space $\A^n - \{0\}$.
Using a dg model for the punctured $n$-space presented in \cite{FHK}, in appendix \ref{appx:A} we construct a dg model for the derived global sections of the tangent bundle over punctured affine space which we will denote by $\lie{witt}(n)$ and refer to as the \defterm{$n$-dimensional Witt algebra}.
Here is a list of important properties of the dg Lie algebra $\lie{witt}(n)$:
\begin{itemize}
\item The underlying cochain complex $\lie{witt}(n)$ is concentrated in cohomological degrees $0,\ldots,n-1$.
\item Its cohomology is concentrated in degrees $0$ and $n-1$.
There is an inclusion of the Lie algebra of vector fields on $\A^n$ (thought of as a dg Lie algebra concentrated in degree zero):
\beqn
\lie{vect}^{alg}(n) = \C[z_1,\ldots,z_n]\{\del_{z_1},\ldots,\del_{z_n}\} \hookrightarrow 
\lie{witt}(n)
\eeqn
which induces an isomorphism in zeroth cohomology.
\item In degree $(n-1)$ \brian{finish}
\end{itemize}

The Virasoro Lie algebra is the unique nontrivial central extension of the Witt algebra $\lie{witt}(1)$.
This central extension admits an interpretation in terms of the Lie algebra cohomology of  vector fields $\lie{vect}(1)$ on the $1$-disk via the isomorphisms
\beqn
H^3(\lie{vect}(1); \C) \cong H^2(\lie{vect}(1); \Omega^1) \cong H^2(\lie{witt}(1);\C) \cong \C .
\eeqn
In the last part of this section we will construct an injective map
\beqn
H^{2n+1}(\lie{vect}(n);\C) \to H^2(\lie{witt}(n);\C), 
\eeqn
thus providing a source of central extensions for the $n$-dimensional Witt algebra.
Our construction of central extensions uses factorization algebras.

\subsection{Central extensions from local cohomology}

Such central extensions originate from the so-called local cohomology of holomorphic vector fields.
We briefly recall the definition of local cohomology from \cite{CG2}.

For $E$ a vector bundle on a manifold $M$, define the space of local functionals to be 
\beqn
\oloc(E) \define {\rm Dens}_M \otimes_{D_M} {\rm Lag} (E) .
\eeqn
Here $\op{Dens}_X$ is the bundle of densities on $M$ and $\op{Lag}(E)$ is the left $D_M$-module of Lagrangians
\beqn
\op{Lag} (E) \define \prod_{n > 0} {\rm Hom}_{C^\infty_M} \left(\op{jet} (E) , C^\infty_M\right) .
\eeqn
Concretely, a Lagrangian is a $C^\infty_M$-valued functional which only depends on jets of sections of $E$, and a local functional is a Lagrangian defined up to total derivatives.
Given a Lagrangian $L = L(\phi)$ we will denote its corresponding local functional by~$\int L(\phi)$.

If $E$ is a complex of vector bundles then $\oloc(E)$ is a sheaf of cochain complexes.
If $\cL = \Gamma(M, L)$ is a local Lie algebra then $\oloc(L[1])$ is equipped with the Chevalley--Eilenberg differential, hence giving a local version of Lie algebra cohomology.
We denote this sheaf of complexes by $C^\bu_{loc}(\cL)$.
Note that for every open set $U \subset M$ there is an embedding map
\beqn\label{eqn:localtocompact}
C^\bu_{loc}(\cL)(U) \hookrightarrow C^\bu(\cL_c(U)) 
\eeqn
where the right hand side is the Chevalley--Eilenberg complex computing the Lie algebra cohomology of compactly supported sections of $L$ on $U$.

The local cohomology for $\cL=\cT_X$ the local Lie algebra of holomorphic vector fields on a complex manifold $X$ has been characterized in \cite{BWgf}.
In the theorem below,~$Fr_X$ denotes the principal $U(n)$-bundle of unitary frames on $X$.

\begin{thm}
Let $Y_n$ be the restriction of the universal principal $U(n)$-bundle to the $2n$-skeleton of $BU(n)$.
Then
\beqn
H^\bu_{loc} (\cT(X)) \cong H^\bu(Fr_X \times^{U(n)} Y_n)[2n] .
\eeqn

In particular, when $X = \C^n$ there are isomorphisms
\beqn
H^\bu_{loc} (\cT(\C^n)) \cong H^\bu(\lie{vect}(n))[2n] \cong H^\bu(Y_n)[2n] .
\eeqn
\end{thm}

We are most interested in the degree one local cohomology.
A simple application of the Serre spectral sequence reveals that in this case 
\beqn
H^1_{loc}(\cT(\C^n)) = H^{2n+1}(\lie{vect}(n)) = H^{2n+2} (BU(n)) .
\eeqn
So, degree one local cohomology classes for $\cT(\C^n)$ are in one-to-one correspondence with degree $2n+2$ polynomials in the universal Chern classes $c_1,\ldots,c_n$.

@@

At this point, we can see how central extensions of the $n$-dimensional Witt algebra appear.
We have pointed out in \eqref{eqn:localtocompact} how local cohomology classes of a local Lie algebra $\cL$ supported on $U$ determine Lie algebra cohomology classes for the Lie algebra of compactly supported sections $\cL_c(U)$.
We showed in appendix \ref{appx:A} that the $n$-dimensional Witt algebra $\lie{witt}(n)$ admits a homomorphism of dg Lie algebras
\beqn
j \colon \lie{witt}(n) \hookrightarrow \Omega^{0,\bu} (\C^n - \{0\}, \T) = \cT(\C^n - \{0\}),
\eeqn
which has the property that in cohomology $H^\bu(j)$ is a dense embedding of topological vector spaces.

We consider the local dg Lie algebra $\Omega^\bu(\R) \otimes \lie{witt}(n)$ defined on the manifold $\R$.
The differential is 
\beqn
\d_{dR} \otimes \id + \id \otimes \dbar_{\lie{witt}},
\eeqn
where the first term is the de Rham operator on $\R$ and the second is the internal differential to the dg Lie algebra $\lie{witt}(n)$.
The bracket is
\beqn\label{eqn:tensorbracket}
[\eta \otimes X, \theta \otimes Y] = (\eta \theta) \otimes [X,Y] , \quad \eta,\theta \in \Omega^\bu(\R), \;\; X,Y \in \lie{witt}(n)
\eeqn
where $[-,-]$ is the Lie bracket in $\lie{witt}(n)$.
Using $j$ we will construct a map (up to homotopy) of the form
\beqn
\til j \colon \Omega^\bu_c (\R) \otimes \lie{witt}(n) \to \cT_c (\C^n - 0)
\eeqn
as follows.

@@

We now construct an $L_\infty$ equivalence 
\beqn
\Phi = (\Phi^{(1)}, \Phi^{(2)}) \colon \Omega^\bu(\R) \otimes \lie{witt}(n) \rightsquigarrow \cL_{log} .
\eeqn
Let $\Phi^{(1)} = \id$ and 
\begin{align*}
\Phi^{(2)}\left(f \d t\otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j} \right) & = fg \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} \\
\Phi^{(2)}\left(f \d t \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j} \right) & = fg \d t \otimes \alpha \beta \left(\lambda_i \frac{\del}{\del z_j} + \lambda_j \frac{\del}{\del z_i} \right) .
\end{align*}
To see that $\Phi = (\Phi^{(1)}, \Phi^{(2)})$ is an $L_\infty$ morphism we observe the following relations:
\begin{multline}
\Phi^{(2)}\left(\d f \otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j}\right) - (-1)^{\alpha} \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , \d g \otimes \beta \frac{\del}{\del z_j}\right) \\ = f g' \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} ,
\end{multline}
and
\begin{multline}
- (\d + \dbar_{\lie{witt}}) \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) + \Phi^{(2)}\left(\d f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) \\ + \Phi^{(2)}\left(f \otimes \dbar \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) - (-1)^\alpha \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \dbar \beta \frac{\del}{\del z_j}\right)  \\ = f g' \d t \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \d t \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} + fg \otimes \alpha (\dbar \lambda_i) \beta \frac{\del}{\del z_j} ,
\end{multline}
where $f,g \in C^\infty(\R)$ and $\alpha \frac{\del}{\del z_i}, \beta \frac{\del}{\del z_j} \in \lie{witt}(n)$.

@@

\begin{prop}
The local dg Lie algebras $\Omega^\bu_\R \otimes \lie{witt}(n)$ and $\cL_{log}$ are $L_\infty$-equivalent.
In particular, the map $\Phi$ defines a quasi-isomorphism of commutative dg algebras
\beqn
\Phi^* \colon C^\bu(\cL_{log,c}(\R)) \xto{\simeq} C^\bu(\Omega^{\bu}_c(\R) \otimes \lie{witt}(n))
\eeqn
which restricts to a quasi-isomorphism
\beqn
\Phi^* \colon C_{loc}^\bu(\cL_{log}) \xto{\simeq} C_{loc}^\bu(\Omega^\bu(\R) \otimes \lie{witt}(n)) .
\eeqn
\end{prop}

Next we define a homomorphism of dg Lie algebras
\beqn
\til j \colon \cL_{log}(\R) \to \cT(\C^n - \{0\})
\eeqn
by the formulas
\begin{align*}
\til j \left(f(t) \otimes \alpha \frac{\del}{\del z_i}\right) & = f(\log z \zbar) \alpha \frac{\del}{\del z_i} \\
\til j \left(f(t) \d t \otimes \alpha \frac{\del}{\del z_i}\right) & = f(\log z \zbar) \dbar (\log z \zbar )\alpha \frac{\del}{\del z_i} .
\end{align*}
It is immediate to verify that this is a cochain map and it is compatible with Lie brackets. (In fact, the complicated form of the Lie bracket defining $\cL_{log}$ was motivated by this embedding.)

\begin{lem}
The cochain map
\beqn
\til j^* \colon C^\bu (\cT_c(\C^n - 0)) \to C^\bu \left(\cL_c(\R) \right)
\eeqn
given by restriction along $\til j$ preserves local cochains. 
Furthermore, if $\phi$ is a local cochain for $\cT(\C^n - 0)$ then $\til j^* \phi$ is translation invariant as a local cochain on $\R$. 
Thus, $\til j$ determines a homomorphism
\beqn
\til j^* \colon C^\bu_{loc}(\cT(\C^n-0)) \to C^\bu_{loc}\left(\cL_{log}\right)^{\R} .
\eeqn
\end{lem}

@@

We recall the construction of the enveloping factorization algebra from \cite{CG2}.
Let $\cE$ be a vector bundle on a manifold $M$ and let $\cE_c$ denote its cosheaf of compactly supported sections.
It is shown in \cite{CG1} how the assignment of the graded vector space
\beqn
\Sym \, \cE_c(U) = \oplus_{n \geq 0} \Gamma_c(U, \Sym^n E)
\eeqn
to an open set $U \subset M$ assemble into a factorization algebra on $M$.

Now, let $\cL = \Gamma(M,L)$ be a local dg Lie algebra on a manifold $M$.
Applying the above construction to $E[-1] = L$ gives rise \cite{CG2} to the factorization algebra which assigns to an open set $U \subset M$ the graded vector space 
\beqn
\Sym \, \cL_c (U) [1] .
\eeqn
For each open set $U$ this graded vector space is equipped with a differential $\d_{CE}$ whose cohomology computes the Lie algebra homology of the dg Lie algebra $\cL_c(U)$.
The resulting dg factorization algebra is denoted by $C_\bu(\cL_c)$ and is called the \defterm{enveloping factorization algebra} associated to the local Lie algebra $\cL$.

>>>>

\usepackage{../macros-master,amsaddr,physics}
\usepackage{mathbbol}

\addbibresource{refs.bib}

\newcommand{\fields}{\cE}
\newcommand{\Vir}{\sV\op{ir}}
\newcommand{\vir}{\lie{vir}}
\setcounter{tocdepth}{1}

\renewcommand{\op}{\operatorname}

@@

Let $X$ b
e a complex manifold of dimension $n$.
The sheaf of holomorphic vector fields has the natural structure of a sheaf of Lie algebras with bracket the Lie bracket of vector fields.
Since this bracket involves only holomorphic differential operators, it extends to a bracket on the Dolbeault complex $\Omega^{0,\bu}(X,\T_X)$ of the holomorphic tangent bundle.
This bracket endows the Dolbeault complex $\Omega^{0,\bu}(X, \T_X)$ with coefficients in the holomorphic tangent bundle with the structure of a dg Lie algebra where the differential is $\dbar$.
Its global sections is an explicit model for the dg Lie algebra $\R\Gamma(X , \cT_X)$ where $\cT_X$ is the sheaf of holomorphic vector fields on $X$.

As defined in \cite{CG2}, a local dg Lie algebra is a $\Z$-graded complex of vector bundles whose sheaf of sections is equipped with the structure of a dg Lie algebra.
Let $\cT_X$ be the local dg Lie algebra whose underlying complex of vector bundles is
\begin{equation}
\Omega^{0,\bu}(X, \T_X) = \Gamma_{C^\infty} \left(X , \wedge^\bu \br \T_X \otimes \T_X \right) .
\end{equation}
The differential is the $\dbar$-operator associated to the holomorphic bundle $\T_X$.
The bracket is the Lie bracket of holomorphic vector fields extended to the Dolbeault complex as described above.
By Dolbeault's theorem, for $U \subset X$ a Stein open set there is a quasi-isomorphism $\cT_X(U) \simeq \op{Vect}^{hol}(U)$, the Lie algebra of holomorphic vector fields on~$U$.
When $X = \C^n$ we denote $\cT_X = \cT$ for simplicity.

@@

The dg Lie algebra $\cT(\C - \{0\})$ is quasi-isomorphic to the Lie algebra of holomorphic vector fields on~$\C^\times$.
Replacing $\C^\times$ by the formal punctured disk gives the Witt algebra $\lie{vect}(D^\times) = \C((z)) \del_z$ whose unique nontrivial central extension is the Virasoro Lie algebra.

For an example of a complex manifold which is not Stein consider $X = \C^n - \{0\}$.
The embedding of dg Lie algebras
\begin{equation}
\Vect^{hol}(\C^n - \{0\}) \hookrightarrow \cT(\C^n - \{0\})
\end{equation}
is no longer a quasi-isomorphism.
This map does define an isomorphism in $H^0$ cohomology, but $\cT(\C^n-\{0\})$ also has cohomology in degree $(n-1)$. 
In standard coordinates, cochain representatives for this cohomology are given by expressions of the form
\begin{equation}
\sum_j \left(\sum_{k_1 \cdots k_n} a^j_{k_1\cdots k_n} L_{\del_{z_1}^{k_1}} \cdots L_{\del_{z_n}^{k_n}} \omega_{BM}\right) \frac{\del}{\del z_j} 
\end{equation}
Here $a^j_{k_1\cdots k_n}$ are constants and $\omega_{BM} \in \Omega^{0,n-1}(\C^n-\{0\})$ is the Bochner--Martinelli form characterized by the formula $\oint_{S^{2n-1}} \omega_{BM} \wedge \d^n z= 1$ with $S^{2n-1}$ any sphere centered at $0 \in \C^n$.

We make the distinction between the complex manifold $\C^n-\{0\}$, the algebraic variety of punctured affine space $\mathring{\A}^{n}=\A^n - \{0\}$, and the punctured formal disk $\mathring{D}^{n}=D^{n}-\{0\}$.
A model for the derived algebra of functions for the complex manifold $\C^{n}-\{0\}$ is the Dolbeault complex $\Omega^{0,\bu}(\C^{n}-\{0\})$.
Using the Jouanolou torsor, an explicit model for the derived algebra of functions on punctured affine space (respectively, formal disk) has been constructed in \cite{FHK} and we will denote it $\sfA_{[n]}$ (respectively, $\sfA_{n}$).
It is an algebraic (respectively, formal) version of the Dolbeault complex of the complex manifold $\C^{n}-\{0\}$.
Similarly, there is an algebraic (respectively, formal) version of $\cT(\C^n - \{0\})$ with $\C^n - \{0\}$ replaced by punctured $n$-dimensional algebraic affine space $\mathring{\A}^{n}$ (respectively, the punctured formal disk $\mathring{D}^{n}$).
In the affine (respectively, formal) case these models are cochain models for the derived global sections of the tangent sheaf $\R \Gamma(\mathring{\A}^{n},\T)$ (respectively, $\R \Gamma(\mathring{D}^{n},\T)$).

Using a dg model for the punctured $n$-space presented in \cite{FHK}, in appendix \ref{appx:A} we construct a dg model for the derived global sections of the tangent bundle over the punctured formal disk which we will denote by $\lie{witt}(n)$ and refer to as the \defterm{$n$-dimensional Witt algebra}.
Here is a list of important properties of the dg Lie algebra $\lie{witt}(n)$:
\begin{itemize}
  \item It is a dg model for $\R \Gamma(\mathring{D}^{n},\T)$.
        The underlying cochain complex $\lie{witt}(n)$ is concentrated in cohomological degrees $0,\ldots,n-1$. In particular, its cohomology is concentrated in degrees $0$ and $n-1$.
  \item We have the following local trivializations.
        Any element of $\xi \in \lie{witt}(n)$ is of the form
        \begin{equation}\label{}
          \xi = \sum_{i=1}^{n} \alpha_{i}(z) \frac{\del}{\del z_{i}}
        \end{equation}
        where $\alpha_{i}(x) \in \sfA_{n}$.
\item There is an inclusion of dg Lie algebras from vector fields on the formal disk $D^n$ (thought of as a dg Lie algebra concentrated in degree zero):
\begin{equation}
\lie{vect}(n) = \op{Der} \, \C[[z_1,\ldots,z_n]] \hookrightarrow
\lie{witt}(n)
\end{equation}
which induces an isomorphism in zeroth cohomology.
\item In degree $(n-1)$ \brian{finish}
\end{itemize}

The Virasoro Lie algebra is the unique nontrivial central extension of the ordinary Witt algebra $\lie{witt}(1)$.
This central extension admits an interpretation in terms of the Lie algebra cohomology of  vector fields $\lie{vect}(1)$ on the $1$-disk via the isomorphisms
\begin{equation}
H^3(\lie{vect}(1); \C) \cong H^2(\lie{vect}(1); \Omega^1) \cong H^2(\lie{witt}(1);\C) \cong \C .
\end{equation}
This is a version of transgression, and in this example it can be understood explicitly as follows.
Consider the dg $\lie{vect}(1)$-module $\Omega^{\bu}$ defined by
\begin{equation}\label{}
  \cO(D) = \C[[z]] \xto{\del} \C[[z]] \d z = \Omega^{1}(D) [-1]
\end{equation}
where the differential is the de Rham differential.
By the formal Poincar\'{e} lemma, there is a quasi-isomorphism of $\lie{vect}(1)$-modules $\C \xto{\simeq} \Omega^{\bu}$ and a map \brian{finish}

Take a class $[\phi] \in H^{3}(\lie{vect}(1))$.

In the last part of this section we will construct a linear map
\begin{equation}
H^{2n+1}(\lie{vect}(n);\C) \to H^2(\lie{witt}(n);\C), 
\end{equation}
thus providing a source of central extensions for the $n$-dimensional Witt algebra.
Our construction of central extensions uses factorization algebras.

\subsection{Local cohomology of vector fields}

Such central extensions originate from the so-called local cohomology of holomorphic vector fields.
We briefly recall the definition of local cohomology from \cite{CG2}.
For details specific to the local Lie algebra of holomorphic vector fields we refer to \cite{BWgf}.

For $E$ a vector bundle on a manifold $M$, define the space of local functionals to be 
\begin{equation}
\oloc(E) = {\rm Dens}_M \otimes_{D_M} {\rm Lag} (E) .
\end{equation}
Here $\op{Dens}_X$ is the bundle of densities on $M$ and $\op{Lag}(E)$ is the left $D_M$-module of Lagrangians
\begin{equation}
\op{Lag} (E) \define \prod_{n > 0} {\rm Hom}_{C^\infty_M} \left( \Sym^n(J^\infty E) , C^\infty_M\right) .
\end{equation}
Concretely, a Lagrangian is a $C^\infty_M$-valued functional which only depends on jets of sections of $E$, and a local functional is a Lagrangian defined up to total derivatives.
Notice that we throw away the constant coefficient Lagrangian densitites.
Given a Lagrangian $L = L(\phi)$ we will denote its corresponding local functional by~$\int L(\phi)$.

If $E$ is a complex of vector bundles then $\oloc(E)$ inherits the differential and is a sheaf of cochain complexes.
If $\cL = \Gamma(M, L)$ is a local Lie algebra then $\oloc(L[1])$ is equipped with the Chevalley--Eilenberg differential, hence giving a local version of Lie algebra cohomology.
We denote this sheaf of cochain complexes by $C^\bu_{loc}(\cL)$.
Note that for every open set $U \subset M$ there is an embedding map
\begin{equation}\label{eqn:localtocompact}
C^\bu_{loc}(\cL)(U) \hookrightarrow C^\bu(\cL_c(U)) 
\end{equation}
where the right hand side is the Chevalley--Eilenberg complex computing the Lie algebra cohomology of compactly supported sections of $L$ on $U$.
The map sends $\int \cL|_{U}$ to the honest integral $\int_{U} \cL$.
Notice that the latter expression is defined by the condition of compact support.

The local cohomology of $\cL=\cT_X$, the local Lie algebra of holomorphic vector fields on a complex manifold $X$, has been characterized in \cite{BWgf}.
In the theorem below,~$Fr_X$ denotes the principal $U(n)$-bundle of unitary frames on $X$.

\begin{thm}[\cite{BWgf}]
Let $Y_n$ be the restriction of the universal principal $U(n)$-bundle to the $2n$-skeleton of $BU(n)$.
Then
\begin{equation}
H^\bu_{loc} (\cT(X)) \cong H^\bu(Fr_X \times^{U(n)} Y_n)[2n] .
\end{equation}

In particular, when $X = \C^n$ there are isomorphisms
\begin{equation}
H^\bu_{loc} (\cT(\C^n)) \cong H^\bu(\lie{vect}(n) ; \C)[2n] \cong H^\bu(Y_n)[2n] ,
\end{equation}
where $H^\bu(\lie{vect}(n) ; \C)$ is the Gelfand--Fuks Lie algebra cohomology of $\lie{vect}(n)$ with trivial coefficients.
\end{thm}

We are most interested in the degree one local cohomology.
A simple application of the Serre spectral sequence reveals that in this case 
\begin{equation}
H^1_{loc}(\cT(\C^n)) \simeq H^{2n+1}(\lie{vect}(n)) \simeq H^{2n+2} (BU(n)) .
\end{equation}
So, degree one local cohomology classes for $\cT$ are in one-to-one correspondence with degree $2n+2$ polynomials in the universal Chern classes $c_1,\ldots,c_n$.

@@

At this point, we can see how central extensions of the $n$-dimensional Witt algebra appear.
The morphism \eqref{eqn:localtocompact} shows how local cohomology classes of a local Lie algebra $\cL$ supported on $U$ determine Lie algebra cohomology classes for the Lie algebra of compactly supported sections $\cL_c(U)$.
We showed in appendix \ref{appx:A} that the $n$-dimensional Witt algebra $\lie{witt}(n)$ admits a homomorphism of dg Lie algebras
\begin{equation}
j \colon \lie{witt}(n) \hookrightarrow \Omega^{0,\bu} (\C^n - \{0\}, \T) = \cT(\C^n - \{0\}),
\end{equation}
which has the property that in cohomology $H^\bu(j)$ is a dense embedding of topological vector spaces.

We consider the local dg Lie algebra $\Omega^\bu(\R) \otimes \lie{witt}(n)$ defined on the manifold $\R$.
The differential is 
\begin{equation}
\d_{dR} \otimes \id + \id \otimes \dbar_{\lie{witt}},
\end{equation}
where the first term is the de Rham operator on $\R$ and the second is the internal differential to the dg Lie algebra $\lie{witt}(n)$.
The bracket is
\begin{equation}\label{eqn:tensorbracket}
[\eta \otimes X, \theta \otimes Y] = (\eta \theta) \otimes [X,Y] , \quad \eta,\theta \in \Omega^\bu(\R), \;\; X,Y \in \lie{witt}(n)
\end{equation}
where $[-,-]$ is the Lie bracket in $\lie{witt}(n)$.
Using $j$ we now construct a map (up to homotopy) of the form
\begin{equation}\label{eqn:tilj}
\til j \colon \Omega^\bu_c (\R) \otimes \lie{witt}(n) \to \cT_c (\C^n - 0) .
\end{equation}

@@

We now construct an $L_\infty$ equivalence 
\begin{equation}
\Phi = (\Phi^{(1)}, \Phi^{(2)}) \colon \Omega^\bu(\R) \otimes \lie{witt}(n) \rightsquigarrow \cL_{log} .
\end{equation}
Let $\Phi^{(1)} = \id$ and 
\begin{align*}
\Phi^{(2)}\left(f \d t\otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j} \right) & = fg \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} \\
\Phi^{(2)}\left(f \d t \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j} \right) & = fg \d t \otimes \alpha \beta \left(\lambda_i \frac{\del}{\del z_j} + \lambda_j \frac{\del}{\del z_i} \right) .
\end{align*}
To see that $\Phi = (\Phi^{(1)}, \Phi^{(2)})$ is an $L_\infty$ morphism we observe the following relations:
\begin{multline}
\Phi^{(2)}\left(\d f \otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j}\right) - (-1)^{\alpha} \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , \d g \otimes \beta \frac{\del}{\del z_j}\right) \\ = f g' \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} ,
\end{multline}
and
\begin{multline}
- (\d + \dbar_{\lie{witt}}) \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) + \Phi^{(2)}\left(\d f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) \\ + \Phi^{(2)}\left(f \otimes \dbar \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) - (-1)^\alpha \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \dbar \beta \frac{\del}{\del z_j}\right)  \\ = f g' \d t \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \d t \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} + fg \otimes \alpha (\dbar \lambda_i) \beta \frac{\del}{\del z_j} ,
\end{multline}
where $f,g \in C^\infty(\R)$ and $\alpha \frac{\del}{\del z_i}, \beta \frac{\del}{\del z_j} \in \lie{witt}(n)$.

@@

\begin{prop}
The local dg Lie algebras $\Omega^\bu_\R \otimes \lie{witt}(n)$ and $\cL_{log}$ are $L_\infty$-equivalent.
In particular, the map $\Phi$ defines a quasi-isomorphism of commutative dg algebras
\begin{equation}
\Phi^* \colon C^\bu(\cL_{log,c}(\R)) \xto{\simeq} C^\bu(\Omega^{\bu}_c(\R) \otimes \lie{witt}(n))
\end{equation}
which restricts to a quasi-isomorphism
\begin{equation}
\Phi^* \colon C_{loc}^\bu(\cL_{log}) \xto{\simeq} C_{loc}^\bu(\Omega^\bu(\R) \otimes \lie{witt}(n)) .
\end{equation}
\end{prop}

Next we define a homomorphism of dg Lie algebras
\begin{equation}
\til j \colon \cL_{log}(\R) \to \cT(\C^n - \{0\})
\end{equation}
by the formulas
\begin{align*}
\til j \left(f(t) \otimes \alpha \frac{\del}{\del z_i}\right) & = f(\log z \zbar) \alpha \frac{\del}{\del z_i} \\
\til j \left(f(t) \d t \otimes \alpha \frac{\del}{\del z_i}\right) & = f(\log z \zbar) \dbar (\log z \zbar )\alpha \frac{\del}{\del z_i} .
\end{align*}
It is immediate to verify that this is a cochain map and it is compatible with Lie brackets. (In fact, the complicated form of the Lie bracket defining $\cL_{log}$ was motivated by this embedding.)

\begin{lem}
The cochain map
\begin{equation}
\til j^* \colon C^\bu (\cT_c(\C^n - 0)) \to C^\bu \left(\cL_{log,c}(\R) \right)
\end{equation}
given by restriction along $\til j$ preserves local cochains. 
Furthermore, if $\phi$ is a local cochain for $\cT(\C^n - 0)$ then $\til j^* \phi$ is translation invariant as a local cochain on $\R$. 
Thus, $\til j$ determines a homomorphism
\begin{equation}
\til j^* \colon C^\bu_{loc}(\cT(\C^n-0)) \to C^\bu_{loc}\left(\cL_{log}\right)^{\R} .
\end{equation}
\end{lem}

@@

We recall the construction of the enveloping factorization algebra from \cite{CG2}.
Let $\cE$ be a vector bundle on a manifold $M$ and let $\cE_c$ denote its cosheaf of compactly supported sections.
It is shown in \cite{CG1} how the assignment of the graded vector space
\begin{equation}
\Sym \, \cE_c(U) = \oplus_{n \geq 0} \Gamma_c(U, \Sym^n E)
\end{equation}
to an open set $U \subset M$ assemble into a factorization algebra on $M$.

Now, let $\cL = \Gamma(M,L)$ be a local dg Lie algebra on a manifold $M$.
Applying the above construction to $E[-1] = L$ gives rise \cite{CG2} to the factorization algebra which assigns to an open set $U \subset M$ the graded vector space 
\begin{equation}
\Sym \, \cL_c (U) [1] .
\end{equation}
For each open set $U$ this graded vector space is equipped with a differential $\d_{CE}$ whose cohomology computes the Lie algebra homology of the dg Lie algebra $\cL_c(U)$.
The resulting dg factorization algebra is denoted by $C_\bu(\cL_c)$ and is called the \defterm{enveloping factorization algebra} associated to the local Lie algebra $\cL$.
